\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
Conclusion modified

%Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
%being better performers than the {\sf TRUE} condition during the interaction phase
%comes from the transparency of the robot's behaviour. The robot's
%behaviour was not at all transparent in the former two conditions. This might
%have caused the participants to put more effort in understanding the behaviour.
%Therefore, they performed better.
\section{Discussion}

We demonstrated that eye-tracking data can provide several process
variables to assess not only the task-based performance of the
participants but also to evaluate HRI. The prime advantage of using
mobile eye-tracking is that the users' interaction with the robot can
still be ecologically valid. On the other hand, using fMRI for
evaluating HRI reduces the interaction to a video of the robot only
~\cite{rosenthal2013neural}.

Another advantage of using mobile eye-tracking to evaluate HRI,
especially in an educational context, is that the data provides direct
and noise free access to the users' attention. While in other
physiological measures for attention, such as EEG, the data has a lot of
noise and the relation to the attention is very task-specific.

@@

\section{Conclusion}

>>>>

%Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
%being better performers than the {\sf TRUE} condition during the interaction phase
%comes from the transparency of the robot's behaviour. The robot's
%behaviour was not at all transparent in the former two conditions. This might
%have caused the participants to put more effort in understanding the behaviour.
%Therefore, they performed better.
\section{Conclusion}

We demonstrated that eye-tracking data can provide several process
variables to assess not only the task-based performance of the
participants but also to analyse HRI situations. The prime advantage of using
mobile eye-tracking is that the users' interaction with the robot can
still be ecologically valid. On the other hand, using fMRI for
evaluating HRI reduces the interaction to a video of the robot only
~\cite{rosenthal2013neural}.

Another advantage of using mobile eye-tracking to assess HRI situations, is that the data provides direct and noise free access to the users' attention. While in other physiological measures for attention, such as EEG, the data has a lot of noise and the relation to the attention is very task-specific.

@@
